---
title: "dottable"
author: "Andrew Hwang"
format: pdf
editor: visual
---

<https://github.com/Hwangster1/dottable>

```{r}
library(tidyverse)

library(dplyr)

library(data.table)

nyc_data <- fread("nycdata.csv")
```

Use and show data.table code to select the variables year, month, day, and hour from the imported flights data

```{r}
selected_flights <- nyc_data[, .(year, month, day, hour)]
str(selected_flights)
```

Use and show data. table code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA

```{r}
filtered_flights <- nyc_data[carrier == "DL" & origin == "JFK" & dest == "SEA"]

str(filtered_flights)
```

Use and show data.table code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
filtered_flights_2 <- nyc_data[carrier == "UA" & month == 3 & air_time < 330]
str(filtered_flights_2)
```

Use and show tidyverse code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
filtered_flights_3 <- nyc_data |>
  filter(carrier == "UA", month == 3, air_time < 330)
head(filtered_flights_3)
```

Use the data.table method to add a variable called speed that is the average air speed of the plane in miles per hour.

```{r}
flights1 <- nyc_data[, speed := (distance / air_time) * 60]
str(flights1)
```

Use the tidyverse method to add a variable called speed that is the average air speed of the plane in miles per hour.

```{r}
flights2 <- nyc_data |>
  mutate(speed = (distance / air_time) * 60)
head(flights2)
```

Show and use coding to change the carrier abbreviation of UA to UniitedAir,

7a. data.table method

```{r}
united_1<- nyc_data[carrier == "UA", carrier := "UnitedAir"]
str(united_1)
```

7b. tidyverse method (Use a sequence of dplyr commands so that you can see the change in your table)

```{r}
united_2 <- nyc_data |>
  mutate(carrier = ifelse(carrier == "UA", "UnitedAir", carrier))
```
